Expected Dependency Pair Match:\\ Predicting translation quality with expected syntactic structure

### 2009-07-29 mtjournal.tex
small clarifications to address some reviewer #2 concerns

\subsection{Dimensions of metric family}
\label{sec:metricdimensions}
In the experiments presented later in this article, we explore the
space of metrics outlined above along multiple dimensions:
\begin{description}
\item[Decompositions.] We consider syntactic decompositions of the
  following types:
  \begin{description}
  \item[dlh] $\left\langle \textrm{Dependent}, \textrm{arc Label},
      \textrm{Head}\right\rangle$ Here, every tuple includes two words
    and the dependency-label between them.
  \item[dl] $\left\langle \textrm{Dependent}, \textrm{arc Label}
      \right\rangle$ The tuple is the word plus the label of the arc
      linking it to its head; this decomposition marks how the word
      fits into its syntactic context (what it modifies).
    \item[lh] $\left\langle \textrm{arc Label}, \textrm{Head}
      \right\rangle$ Each tuple here is the dependency relation plus
      the word being modified; this decomposition implicitly marks how
      key the word is to the sentence.
    \item[dh] $\left\langle \textrm{Dependent}, \textrm{Head}
      \right\rangle$ This decomposition drops the arc from the
      dependency-pair tuple, ignoring the syntactic-role information
      implied in the arc labels.
    \item[1g,2g] These decompositions are syntactically-null.  They
      simply include each 1-gram (or 2-gram) without any syntactic
      labeling at all.  They are thus simple measures of unigram
      (bigram) precision and recall.
  \end{description}
\item[Size of $n$-best list.] Although the parser can generate
  considerably more, we consider $n$-best lists of size 1 and of size
  50.
\item[Confidence of $n$-best hypotheses.] An expectation requires a
  probability distribution over the $n$-best list, and we consider
  three options: uniform, the parser probabilities, and a flattened
  version of the parser probabilities such that $\tilde{p}(x) =
  \frac{p(x)^\gamma}{\sum_ip(i)^\gamma}$ (where $\gamma$ is a free
  parameter) to account for the fact that the parser tends to be
  over-confident.  In all cases, the probabilities are normalized to
  sum to one over the the $n$-best list, where the maximum $n$ in this
  work is 50.  The uniform distribution ($\gamma = 0$) is intended to
  be equivalent to the \cite{owczarzak07evaluatingmt}
  \textbf{d\_50} and \textbf{d\_50\_pm} measures.\endnote{
    \inlinecite{owczarzak07evaluatingmt} report no use of parse
    confidence weights, and \textbf{d\_50} and \textbf{d\_50\_pm}
    return the best-matching pair of trees rather than an aggregate
    over the tree sets.}
\item[Score combination.] We consider three possible methods for
  combining scores across decompositions, as suggested in
  section~\ref{sec:approach}:
  \begin{description}
  \item[$F\lbrack\cdot\rbrack$] treats each decomposition as
    contributing $n$ more items to the bag of tokens extracted from
    the tree, and then computes a global $F$ score.
  \item[$\mu_{PR}\lbrack\cdot\rbrack$] constructs a precision and
    recall score from each decomposition, and then does an
    evenly-weighted harmonic mean of all the component precision and
    recall scores.
  \item Tuned, like the previous combination, calculates precision and
    recall separately for each decomposition, but performs a linear
    weighted combination of the resulting precision and recall scores.
    For this tuning, we note that TERp \cite{snover09terp} provides a
    tuneable system over a small number of parameters (they include,
    among others, separate cost for insertions, deletions,
    substitutions and synonyms) and an optimization algorithm that
    assigns weights to each parameter. We use the various
    decompositions' precision and recall as new parameters to the TERp
    optimizer.
  \end{description}
\end{description}

@@

In table~\ref{tab:facorr:combinations}, we compare among several other
members of the DPM family. 
 \begin{table}
  \begin{tabular*}{2.5in}{lr}
    \hline
    metric  &    \multicolumn{1}{c}{$r$} \\
    \hline
    $F[1g,2g,dl,lh]$      &  0.237 \\
    $\mu_{PR}[1g,2g,dl,lh]$ &  0.217 \\
    \rlcline{1-1} \rlcline{2-2}
    $F[1g,2g]$            & 0.227 \\
    $\mu_{PR}[1g,2g]$            & 0.215 \\
%    $F[1g,dl,dlh]$        & 0.227 \\
    \rlcline{1-1} \rlcline{2-2}
    $F[dl,lh]$            &  0.226 \\
    $\mu_{PR}[dl,lh]$      &  0.208 \\
    \hline
  \end{tabular*}
  \caption{Correlation with human fluency/adequacy judgments. Comparing combination methods $F[\cdot]$ and
    $\mu_{PR}[\cdot]$, and comparing the $1g,2g,dl,lh$ decomposition
    with the $dl,lh$ decomposition and other decompositions.}
  \label{tab:facorr:combinations}
\end{table}
Here, we find that combining the decompositions naively in $F[\cdot]$
(before computing precision and recall) has a better $r$ than the
harmonic mean of precision and recall subscores in $\mu_{PR}[\cdot]$.
We also see that we can combine the benefits of string-local $n$-grams
($F[1g,2g]$) with the benefits of dependency information ($F[dl,lh]$)
for a further improved correlation with human judgment, with the best
correlation in $F[1g,2g,dl,lh]$. Including progressively larger chunks
of the dependency graph with $F[1g,dl,dlh]$ (not shown in table, but inspired by
the BLEU$_k$ idea of progressively larger $n$-grams) does not seem to
be an improvement over $F[dl,lh]$.

>>>>

\subsection{Dimensions of metric family}
\label{sec:metricdimensions}
In the experiments presented later in this article, we explore the
space of metrics outlined above along multiple dimensions:
\begin{description}
\item[Decompositions.] We consider syntactic decompositions of the
  following types:
  \begin{description}
  \item[dlh] $\left\langle \textrm{Dependent}, \textrm{arc Label},
      \textrm{Head}\right\rangle$ Here, every tuple includes two words
    and the dependency-label between them.
  \item[dl] $\left\langle \textrm{Dependent}, \textrm{arc Label}
      \right\rangle$ The tuple is the word plus the label of the arc
      linking it to its head; this decomposition marks how the word
      fits into its syntactic context (what it modifies).
    \item[lh] $\left\langle \textrm{arc Label}, \textrm{Head}
      \right\rangle$ Each tuple here is the dependency relation plus
      the word being modified; this decomposition implicitly marks how
      key the word is to the sentence.
    \item[dh] $\left\langle \textrm{Dependent}, \textrm{Head}
      \right\rangle$ This decomposition drops the arc from the
      dependency-pair tuple, ignoring the syntactic-role information
      implied in the arc labels.
    \item[1g,2g] These decompositions are syntactically-null.  They
      simply include each 1-gram (or 2-gram) without any syntactic
      labeling at all.  They are thus simple measures of unigram
      (bigram) precision and recall.
  \end{description}
\item[Size of $n$-best list.] Although the parser can generate
  considerably more, we consider $n$-best lists of size 1 and of size
  50.
\item[Confidence of $n$-best hypotheses.] An expectation requires a
  probability distribution over the $n$-best list, and we consider
  three options: uniform, the parser probabilities, and a flattened
  version of the parser probabilities such that $\tilde{p}(x) =
  \frac{p(x)^\gamma}{\sum_ip(i)^\gamma}$ (where $\gamma$ is a free
  parameter) to account for the fact that the parser tends to be
  over-confident.  In all cases, the probabilities are normalized to
  sum to one over the the $n$-best list, where the maximum $n$ in this
  work is 50.  The uniform distribution ($\gamma = 0$) is intended to
  be equivalent to the \cite{owczarzak07evaluatingmt}
  \textbf{d\_50} and \textbf{d\_50\_pm} measures.\endnote{
    \inlinecite{owczarzak07evaluatingmt} report no use of parse
    confidence weights, and \textbf{d\_50} and \textbf{d\_50\_pm}
    return the best-matching pair of trees rather than an aggregate
    over the tree sets.}
\item[Score combination.] We consider three possible methods for
  combining scores across decompositions, as suggested in
  section~\ref{sec:approach}:
  \begin{description}
  \item[$F\lbrack\cdot\rbrack$] treats each decomposition as
    contributing $n$ more items to the bag of tokens extracted from
    the tree, and then computes a global $F$ score.
  \item[$\mu_{PR}\lbrack\cdot\rbrack$] constructs a precision and
    recall score from each decomposition, and then does an
    evenly-weighted harmonic mean of all the component precision and
    recall scores.
  \item Tuned weight combination, like the previous $\mu_{PR}$
    combination, calculates precision and
    recall separately for each decomposition but performs a linear
    weighted combination of the resulting precision and recall scores.
    For this tuning, we note that TERp \cite{snover09terp} provides a
    tuneable system over a small number of parameters (they include,
    among others, separate cost for insertions, deletions,
    substitutions and synonyms) and an optimization algorithm that
    assigns weights to each parameter. We use the various
    decompositions' precision and recall as new parameters to the TERp
    optimizer.
  \end{description}
\end{description}

@@

In table~\ref{tab:facorr:combinations}, we compare among several other
members of the DPM family. 
 \begin{table}
  \begin{tabular*}{2.5in}{lr}
    \hline
    metric  &    \multicolumn{1}{c}{$r$} \\
    \hline
    $F[1g,2g,dl,lh]$      &  0.237 \\
    $\mu_{PR}[1g,2g,dl,lh]$ &  0.217 \\
    \rlcline{1-1} \rlcline{2-2}
    $F[1g,2g]$            & 0.227 \\
    $\mu_{PR}[1g,2g]$            & 0.215 \\
%    $F[1g,dl,dlh]$        & 0.227 \\
    \rlcline{1-1} \rlcline{2-2}
    $F[dl,lh]$            &  0.226 \\
    $\mu_{PR}[dl,lh]$      &  0.208 \\
    \hline
  \end{tabular*}
  \caption{Correlation with human fluency/adequacy judgments. Comparing combination methods $F[\cdot]$ and
    $\mu_{PR}[\cdot]$, and comparing the $1g,2g,dl,lh$ decomposition
    with the $dl,lh$ decomposition and other decompositions.}
  \label{tab:facorr:combinations}
\end{table}
Here, we find that combining the decompositions naively in $F[\cdot]$
(before computing precision and recall) has a better $r$ than the
harmonic mean of precision and recall subscores in $\mu_{PR}[\cdot]$.
In fact, $F[\cdot]$ measures always outperform the BLEU baseline (from
table~\ref{tab:facorr:subgraphs}), and $\mu_{PR}[\cdot]$ measures are
never better than BLEU.
We also see that we can combine the benefits of string-local $n$-grams
($F[1g,2g]$) with the benefits of dependency information ($F[dl,lh]$)
for a further improved correlation with human judgment, with the best
correlation in $F[1g,2g,dl,lh]$. Including progressively larger chunks
of the dependency graph with $F[1g,dl,dlh]$ (not shown in table, but inspired by
the BLEU$_k$ idea of progressively larger $n$-grams) does not seem to
be an improvement over $F[dl,lh]$.
